---
title: "Figures and Scripts"
---

Summary: This notebook contains code to replicate all figures and tables.


```{r initialize}
## library packages 
library(tidyverse)
library(networkreporting)
library(socviz)
library(cowplot)


## load survey  
survey <- read_csv("../data/full_survey.csv", guess_max = 15000)

## load estimates (money lost, direct, generalized network scale-up)
direct_estimates <- read_csv("../data/results/direct_estimates.csv") 
gnsum_estimates <- read_csv("../data/results/gnsum_estimates.csv") 
loss_estimates <- read_csv("../data/results/money_lost.csv") 

## read in data 
estimates_all_sources <- read_csv("../data/misc/cybercrime_estimates_all_sources.csv")
```

## Figure 1 

Distribution of money lost per directly-reported cybercrime incident.

```{r figure 1}
## select money lost variables 
money_lost <- survey %>% 
  select(id, nondelivery_money, nonpayment_money, extortion_money, banking_money, advanced_fee_money, overpayment_money)

money_lost <- pivot_longer(money_lost, cols = -id, names_to = c('incident', ".value"), 
                           #1+ non digits followed by 1+ digits
                           names_pattern = "(\\D+)_(\\D+)")

## Histogram of money lost
## remove the two cases greater than 5,000
money_plot <- money_lost %>% 
  mutate(money = case_when(
    money > 1500 ~ 1500,
    TRUE ~ money
  )) %>% 
  mutate(incident = case_when(
    incident == "banking" ~ "Banking / Credit Card",
    incident == "nondelivery" ~ "Non-Delivery",
    incident == "banking.lostmoney" ~ "Credit Card / Banking (Lost Money)",
    incident == "advanced_fee" ~ "Advanced Fee",
    incident == "nonpayment" ~ "Non-Payment",
    incident == "extortion" ~ "Extortion",
    incident == "overpayment" ~ "Overpayment"
  )) %>% 
  filter(!is.na(money)) %>% 
  ggplot(aes(x = money, y = ..density..)) +
  stat_density() + 
  theme_bw(base_size = 25) +
  facet_wrap(~incident, nrow = 3) + 
  labs(
    x = "Money Lost",
    Y = "Count"
  ) + 
  scale_x_continuous(breaks=c(0, 500, 1000, 1500),
                   labels=c("0", "500", "1000", "1500+")) + 
  theme(panel.spacing.x=unit(3, "lines"))

## save plot 
ggsave(plot = money_plot, "../figures/fig-money_lost.pdf", height = 10, width = 10)
```

## Figure 2 

Estimates of cybercrime prevalence based both on our direct (blue circle) and network scale-up (red triangle) surveys with 95% confidence intervals. 

```{r fig 2}
## results 
results <- bind_rows(direct_estimates, gnsum_estimates)

## Figure 2 
combined_comparison_plot <- results %>% 
  ggplot(
    mapping = aes(x = reorder(scam, -estimate_annualized),
                  y = estimate_annualized, color = method, shape = method )) + 
  geom_pointrange(position = position_dodge(width = .15), mapping = aes(ymin = low_annualized,
                                                                       ymax = upper_annualized),
                  stroke = 2, size = 1) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_bw(base_size = 22) + 
  labs(x = "",
       y = "Count") +
  scale_y_continuous(label = scales::percent) + 
  theme(legend.position = "bottom") + 
  theme(legend.title =element_blank()) +
  ggsci::scale_color_lancet() + 
  theme(axis.text.x = element_text(angle = -30, vjust = 0.1, hjust=.09)) + 
  theme(
    legend.position = c(.999, .999),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6),
    legend.background = element_rect(color = "black", size = .5, linetype = "solid")) +
  theme(plot.margin=unit(c(1,2,1,.3),"cm"))
 
ggsave(plot = combined_comparison_plot, filename = "../figures/fig-direct_nsum_comparison_combined.pdf", width = 10, height = 9)
```

## Figure 3 

Comparison of cybercrime prevalence estimates generated from different data sources:

```{r}
## organize factors 
estimates_all_sources <- estimates_all_sources %>% 
  filter(!(scam == "Banking / Credit Card" & source == "FTC Consumer Sentinel")) %>%
  mutate(source = as.factor(source)) %>% 
  mutate(source = forcats::fct_relevel(source, "This Study: Direct", "This Study: Generalized Scale-up", "E-CRIME", "Crime UK","DOJ",  "FBI IC3"))

pooled_comparison <- estimates_all_sources %>% 
  filter(scam != "Non-delivery + Non-Payment") %>%
  # filter(scam %in% c("Banking / Credit Card", "Banking / Credit Card (and lost money)", "Non-Delivery")) %>% 
  filter(!is.na(annualized)) %>% 
  ggplot(mapping = aes(x = reorder(scam, annualized),
                  y = annualized, color = source, shape = source, group = source)) + 
  geom_point(mapping = aes(y = annualized), size = 4, stroke = 2, position = position_dodge(width = 0.45)) + 
  scale_shape_manual(values = c(1, 2, 5, 0, 6, 4, 3)) +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  coord_flip() + 
  theme_bw(base_size = 22) + 
  labs(x = "",
       y = "Prevalence (%)",
       title = "") + 
  theme(legend.title =element_blank())  +
  ggsci::scale_color_lancet() +
  theme(
    legend.position = c(.999, 0.001),
    legend.justification = c("right", "bottom"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6),
    legend.background = element_rect(color = "black", size = .5, linetype = "solid"))

pooled_comparison

ggsave(plot = pooled_comparison, filename = "../figures/fig-cybercrime_pooled_comparison.pdf", width = 12, height = 12)
```


## Figure S1

```{r}
## read in populations of known size 
groups_known_size <- read_csv("../data/known_popsize/groups_known_size.csv") %>% 
  mutate(name = tolower(paste0("name_", name)))

## filter for network size 
survey_general <- survey %>% 
  filter(p_over == 1)

## top code
top_code <- function(x) {
  x <- case_when(
    x > 30 ~ 30,
    TRUE ~ x
  )
}

## top code survey
survey_general <- survey_general %>%
  mutate(across(c(starts_with("name")), top_code))


## estimate of adults in the US over age 18 
tot.pop.size <- 328239523 * (1-0.223)

## set vector so we can use with our package
kp.vec <- df.to.kpvec(groups_known_size, kp.var="name", kp.value="size")

## estimate person network size
degree <- kp.degree.estimator(survey.data=survey_general,
                              known.popns=kp.vec,
                              total.popn.size=tot.pop.size,
                              missing="complete.obs")

## add degree
survey_general$degree <- degree

## run internal validity checks using the networkreporting package
iv.result <- nsum.internal.validation(survey.data=survey_general,
                                      weights = "weight",
                                      known.popns=kp.vec,
                                      missing="complete.obs",
                                      killworth.se=TRUE,
                                      total.popn.size=tot.pop.size,
                                      kp.method=TRUE,
                                      return.plot=TRUE)

iv_results <- iv.result$results %>% 
  mutate(name = socviz::prefix_strip(name, prefixes = "name_")) %>% 
  ggplot(aes(x = known.size, y = nsum.holdout.est)) + 
  theme_cowplot() +
  scale_y_continuous(label = scales::comma, limits = c(0, 500000)) + 
  scale_x_continuous(label = scales::comma, limits = c(0, 500000)) + 
  geom_text(aes(label = name)) + 
  geom_abline(slope = 1) + 
  labs(x = "Known Population Size",
       y = "Hold-out Estimate of Popn Size",
       title = "")

iv_results_error_bars <- iv.result$results %>% 
  mutate(name = socviz::prefix_strip(name, prefixes = "name_")) %>% 
  ggplot(aes(x = known.size, y = nsum.holdout.est)) + 
  theme_cowplot() + 
  scale_y_continuous(label = scales::comma, limits = c(0, 500000)) + 
  scale_x_continuous(label = scales::comma, limits = c(0, 500000)) + 
  geom_abline(slope = 1) + 
  geom_errorbar(aes(ymin = nsum.holdout.est - 1.96*killworth.se, 
                    ymax = nsum.holdout.est + 1.96*killworth.se), width = 12000, size = .5) + 
  geom_point(shape = 1, size = 2) +
  labs(x = "Known Population Size",
       y = "",
       title = "") 

internal_consitency_check <- cowplot::plot_grid(iv_results, iv_results_error_bars, labels = "auto")

ggsave(plot = internal_consitency_check, filename = "../figures/fig-hold_out_estimate.pdf", width = 12, height = 5)
```


