---
title: "Generate Tables"
---

Summary: Generate tables for cybercrime release. 

```{r initialize}
## load packages and helper functions 
library(here)
source(here("code", "helpers.R"))
```


```{r}
## load survey  
survey <- read_csv("../data/full_survey.csv", guess_max = 15000)

## load estimates (money lost, direct, generalized network scale-up)
direct_estimates <- read_csv("../data/results/direct_estimates.csv") 
gnsum_estimates <- read_csv("../data/results/gnsum_estimates.csv") 
loss_estimates <- read_csv("../data/results/money_lost.csv") 

## load data 
estimates_all_sources <- read_csv("../data/misc/cybercrime_estimates_all_sources.csv")

## load adjustment factors estimates 
adjustments_pooled <- read_csv("../data/results/nsum_pooled_adjustments.csv")
adjustments_individual <- read_csv("../data/results/nsum_individual_adjustments.csv")
```

## Table 1 
```{r table 1}
## create table 1 
table1 <- direct_estimates %>% 
  select(scam, direct_estimate = estimate_annualized) %>% 
  mutate(direct_estimate = direct_estimate*100) %>% 
  left_join(loss_estimates %>% 
  select(scam, median, q10, q90)) %>% 
  arrange(desc(direct_estimate))  %>% 
  mutate(scam = forcats::fct_relevel(scam, "Banking / Credit Card", "Banking / Credit Card (Lost Money)", "Non-Delivery", "Advanced Fee","Non-Payment",  "Extortion", "Overpayment")) %>% 
  arrange(scam) %>% 
  mutate(across(where(is.numeric), round, 3))

table1 <- gt(data = table1) %>% 
  cols_label(
    "scam" = "Cybercrime",
    "direct_estimate" = "Direct Estimate (%)",
    "median" = "Median",
    "q10" = "Q10",
    "q90" = "Q90",
  ) %>% 
  cols_align("left") %>% 
  tab_spanner(
    label = "Prevalence",
    columns = vars(
      direct_estimate)) %>% 
  tab_spanner(
    label = "Money Lost (Dollars)",
    columns = vars(
      median, q10, q90))

table1 %>%
  gtsave("table_1.tex", path = "../tables/")
```

## Table 2

Annualized cybercrime prevalence from our direct estimation and network scale-up survey. 

```{r table 1}
table2 <- direct_estimates %>% 
  select(cybercrime = scam, direct_estimate = estimate_annualized) %>% 
  left_join(gnsum_estimates %>% 
  select(cybercrime = scam, network_scaleup = estimate_annualized)) %>% 
  select(cybercrime, network_scaleup, direct_estimate) %>% 
  mutate(network_scaleup = round(network_scaleup*100, digits = 3), 
         direct_estimate = round(direct_estimate *100, digits = 3)) %>% 
  mutate(cybercrime = forcats::fct_relevel(cybercrime, "Banking / Credit Card", "Banking / Credit Card (Lost Money)", "Non-Delivery", "Advanced Fee","Non-Payment",  "Extortion", "Overpayment")) %>% 
  arrange(cybercrime)

table2 <- gt(data = table2) %>% 
  cols_label(
    "cybercrime" = "Cybercrime",
    "network_scaleup" = "Network Scale-up (%)",
    "direct_estimate" = "Direct (%)",
  ) %>% 
  opt_row_striping(row_striping = T) %>% 
  cols_align("left")

table2 %>%
  gtsave("table_2.tex", path = "../tables/")
```

## Table S3 

Sample descriptive statistics (unweighted). Sample collected from NORC's Amerispeak Panel. 


```{r}
## recode data  
survey_recode <- survey %>% 
  mutate(
    gender = case_when(
      gender == 1	~ "Male",
      gender == 2	~ "Female"),
    age = case_when(
      age4 == 1 ~	"18-29",
      age4 ==  2	~ "30-44",
      age4 ==  3	~ "45-59",
      age4 ==  4 ~	"60+"),
    race = case_when(
      racethnicity == 1	~ "White, non-Hispanic",
      racethnicity == 2	~ "Black, non-Hispanic",
      racethnicity == 3 ~ "Other, non-Hispanic",
      racethnicity == 4	~ "Hispanic",
      racethnicity == 5	~ "2+, non-Hispanic",
      racethnicity == 6	~ "Asian, non-Hispanic"), 
    income = case_when( 
      income %in% 1:6	~   "<$29,999",
      income %in% 7:11	~ "$30,000 to $74,999",
      income %in% 12:14	~ "$75,000 to $124,999",
      income %in% 15:18	~ ">$125,000+"),
    metro = case_when(
      metro == 0 ~ "Non-Metro Area",
      metro == 1 ~ "Metro Area"),
    marital = as.factor(case_when(
      marital == 1 ~	"Married",
      marital == 2 ~	"Widowed",
      marital == 3 ~	"Divorced",
      marital == 4 ~	"Separated",
      marital == 5 ~	"Never married",
      marital == 6 ~	"Living with partner")), 
    educ = case_when(
      educ == 1	~ "<HS Equivalent",
      educ == 2	~ "HS Equivalent",
      educ == 3	~ "Some college",
      educ == 4	~ "Bachelors",
      educ == 5	~ "Advanced degree")) 

gen <- survey_recode %>% 
  filter(p_over == 1) %>% 
  select(id, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, Marital = marital) %>%
  pivot_longer(-id ) %>% 
  group_by(name, value) %>%
  tally() %>%            
  mutate(prop = round(100*prop.table(n), 1)) %>% 
  rename(n_gen = n, prop_gen = prop)

oversample <- survey_recode %>% 
  filter(p_over == 2) %>% 
  select(id, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, Marital = marital) %>%
  pivot_longer(-id ) %>% 
  group_by(name, value) %>%
  tally() %>%           
  mutate(prop = round(100*prop.table(n), 1))  %>% 
  rename(n_oversample = n, prop_oversample = prop)

total <- survey_recode %>% 
  select(id, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, Marital = marital) %>%
  pivot_longer(-id ) %>% 
  group_by(name, value) %>%
  tally() %>% 
  mutate(prop = round(100*prop.table(n), 1))

unweighted_data <- gen %>% 
  inner_join(oversample, by = c("name", "value")) %>% 
  inner_join(total, by = c("name", "value")) %>% 
 # mutate(name = as.factor(name), value = as.factor(name)) %>% 
  mutate(name = factor(name, levels = c("Gender", "Age", "Education", "Race", "Income", "Metro", "Marital"))) %>% 
  mutate(value = factor(value, levels = c('Male', 'Female',
                                      '18-29', '30-44', '45-59', '60+',
                                      '<HS Equivalent', "HS Equivalent", "Some college", "Bachelors", "Advanced degree",
                                      "White, non-Hispanic", "Black, non-Hispanic", "Other, non-Hispanic", "Hispanic", "2+, non-Hispanic", "Asian, non-Hispanic",
                                      "<$29,999", "$30,000 to $74,999", "$75,000 to $124,999", ">$125,000+",
                                      "Non-Metro Area", "Metro Area",
                                      "Married", "Widowed", "Divorced", "Separated", "Never married", "Living with partner"))) %>% 
  arrange(name, value) 

## create table 
table_s3 <- gt(data = unweighted_data) %>% 
  tab_spanner(
    label = "General Pop",
    columns = vars(
      n_gen, prop_gen)) %>% 
  tab_spanner(
    label = "Oversample",
    columns = vars(
      n_oversample, prop_oversample)) %>% 
  tab_spanner(
    label = "Total",
    columns = vars(
      n, prop)) %>% 
  cols_label(
    "n_gen" = "No.",
    "prop_gen" = "%",
    "n_oversample" = "No.",
    "prop_oversample" = "%",
    "n"  = "No.",
    "prop" = "%",
    value = ""
  ) %>% 
  row_group_order(
      groups = c("Gender", "Age", "Education", "Race")
    ) %>% 
  tab_style(
    style = list(
      cell_text(weight = "bold")),
    locations = cells_row_groups()
  ) %>% 
  opt_row_striping(row_striping = T) %>% 
  cols_align("left")

table_s3 %>%
  gtsave("table_s3.tex", path = "../tables/")
```

## Table S4

Sample descriptive statistics (weighted). Sample collected from NORC's Amerispeak Panel. 

```{r}
gen_weighted <- survey_recode %>% 
  filter(p_over == 1) %>% 
  select(id, weight, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, "Marital Status" = marital) %>%
  pivot_longer(-c(id, weight)) %>% 
  group_by(name, value) %>%
  summarize(n = sum(weight)) %>%            
  mutate(prop = round(100*prop.table(n), 1),
         n = round(n, 0)) %>% 
  rename(n_gen = n, prop_gen = prop)

oversample_weighted <- survey_recode %>% 
  filter(p_over == 2) %>% 
  select(id, weight2, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, "Marital Status" = marital) %>%
  pivot_longer(-c(id, weight2)) %>% 
  group_by(name, value) %>%
  summarize(n = sum(weight2)) %>%            
  mutate(prop = round(100*prop.table(n), 1),
         n = round(n, 0))  %>% 
  rename(n_oversample = n, prop_oversample = prop)

total_weighed <- survey_recode %>% 
  select(id, weight2, Gender = gender, Age = age, Education = educ, Race = race, Income = income, Metro = metro, "Marital Status" = marital) %>%
  pivot_longer(-c(id, weight2)) %>% 
  group_by(name, value) %>%
  summarize(n = sum(weight2)) %>%            
  mutate(prop = round(100*prop.table(n), 1),
         n = round(n, 0))

weighted_data <- gen_weighted %>% 
  inner_join(oversample_weighted, by = c("name", "value")) %>% 
  inner_join(total_weighed, by = c("name", "value")) %>% 
 # mutate(name = as.factor(name), value = as.factor(name)) %>% 
  mutate(name = factor(name, levels = c("Gender", "Age", "Education", "Race", "Income", "Metro", "Marital Status"))) %>% 
  mutate(value = factor(value, levels = c('Male', 'Female',
                                      '18-29', '30-44', '45-59', '60+',
                                      '<HS Equivalent', "HS Equivalent", "Some college", "Bachelors", "Advanced degree",
                                      "White, non-Hispanic", "Black, non-Hispanic", "Other, non-Hispanic", "Hispanic", "2+, non-Hispanic", "Asian, non-Hispanic",
                                      "<$29,999", "$30,000 to $74,999", "$75,000 to $124,999", ">$125,000+",
                                      "Non-Metro Area", "Metro Area",
                                      "Married", "Widowed", "Divorced", "Separated", "Never married", "Living with partner"))) %>% 
  arrange(name, value) 

## create table 
table_s4 <- gt(data = weighted_data) %>% 
  tab_spanner(
    label = "General Pop",
    columns = vars(
      n_gen, prop_gen)) %>% 
  tab_spanner(
    label = "Oversample",
    columns = vars(
      n_oversample, prop_oversample)) %>% 
  tab_spanner(
    label = "Total",
    columns = vars(
      n, prop)) %>% 
  cols_label(
    "n_gen" = "No.",
    "prop_gen" = "%",
    "n_oversample" = "No.",
    "prop_oversample" = "%",
    "n"  = "No.",
    "prop" = "%",
    value = ""
  ) %>% 
  row_group_order(
      groups = c("Gender", "Age", "Education", "Race")
    ) %>% 
  tab_style(
    style = list(
      cell_text(weight = "bold")),
    locations = cells_row_groups()
  ) %>% 
  opt_row_striping(row_striping = T) %>% 
  cols_align("left")

table_s4 %>%
  gtsave("table_s4.tex", path = "../tables/")
```

## Table S6

```{r}
table_s6 <- adjustments_individual %>% 
  mutate(across(where(is.numeric), round, 5)) %>% 
  mutate(Cybercrime = forcats::fct_relevel(Cybercrime, "Banking / Credit Card", "Banking / Credit Card (Lost Money)", "Non-Delivery", "Advanced Fee","Non-Payment",  "Extortion", "Overpayment")) %>% 
  arrange(Cybercrime) %>% 
  gt()

table_s6 %>%
  gtsave("table_s6.tex", path = "../tables/")
```


## Table S7

```{r}
table_s7 <- adjustments_pooled %>%
  mutate(`Adjustment Factor` = (1/degree_ratio) * (1/true_positive_rate)) %>% 
  select(Category = Incidence, `Degree Ratio` = degree_ratio, `Visibility Factor` = true_positive_rate, `Adjustment Factor`) %>% 
  mutate(across(where(is.numeric), round, 5)) %>% 
  gt()

table_s7 %>%
  gtsave("table_s7.tex", path = "../tables/")
```

```{r}
direct_estimates %>% 
  select(scam, direct_estimate = estimate_annualized) %>% 
  left_join(loss_estimates %>% 
  select(scam, median, q10, q90)) %>% 
  summarize(typical_loss = sum(direct_estimate * median, na.rm = T),
            worst_case_loss = sum(direct_estimate * q90, na.rm = T))
```

