---
title: "Demographic Models"
---

Summary: Exploratory code to fit (logistic) models. Specifically, the models look at the association between demographic characteristics and whether someone was the victim of a cybercrime.

Notes: 

- I survey weights for all models (`weight` for genpop, `weight2` for oversample)
- Codebook with variable descriptions and value labels available under: "data/amerispeak/codebook.csv"
- Banking, nondelivery, nonpayment, overpayment, extortion, and advanced fee variables all 1/0 dummy variables indicating whether someone reported being a victim of a scam (and we agreed with our coding).


```{r}
## load packages and helper functions 
library(here)
source(here("code", "helpers.R"))
```
 
```{r}
## read in general survey
survey_full <- read_csv("../data/full_survey.csv", guess_max = 15000) %>% filter(p_over == 1)
survey_oversample <- read_csv("../data/full_survey.csv", guess_max = 15000)

prep_data <- function(df){
  df <- df %>%  
    mutate(age4 = case_when(
      age4 == 1 ~	"18-29",
      age4 == 2	~ "30-44",
      age4 == 3	~ "45-59",
      age4 == 4	~ "60+"),
      educ = case_when(
        educ == 1:2 ~	"High school Or Less",
        educ == 3 ~	"Some College",
        educ == 4:5 ~	"Bachelors or Higher"
      ),
      gender = case_when(
        gender == 1 ~"Male",
        gender == 2 ~ "Female"
      ),
      racethnicity = case_when(
        racethnicity == 1 ~ "White, non-Hispanic",
        racethnicity == 2 ~	"Black, non-Hispanic",
        racethnicity == 4 ~	"Hispanic",
        racethnicity %in% c(3, 5, 6) ~	"Race, Other")
    ) %>%
    mutate(payment_victim = case_when(
      banking == 1 | nondelivery == 1 ~ 1, #| nonpayment == 1 | overpayment == 1 | extortion == 1 | advanced_fee == 1 ~ 1,
      TRUE ~ 0),
      seller_victim = case_when(
        nonpayment == 1 | overpayment == 1 ~ 1,
        TRUE ~ 0),
      scam_victim = case_when(
        extortion == 1 | advanced_fee == 1 ~ 1,
        TRUE ~ 0),
      internet_skills = case_when(
        (skill_advanced_search + skill_pdf + skill_spyware + skill_wiki + skill_cache + skill_phishing)/5 > 3 ~ "High Internet Skills",
        TRUE ~ "Low Internet Skills"),
      internet_skills_continuous = (skill_advanced_search + skill_pdf + skill_spyware + skill_wiki + skill_cache + skill_phishing)/5, 
      income3 = case_when(
        income %in% 1:9 ~ "Less than 50k", ## <50k
        income %in% 10:13 ~ "50 - 100k", ## 50 - 100k
        income %in% 14:18 ~ "100k+" ## 100k+
      )) %>% 
    mutate(gender = fct_relevel(as_factor(gender), "Male"),
           racethnicity = fct_relevel(as_factor(racethnicity), "White, non-Hispanic"),
           educ = fct_relevel(as_factor(educ), "High school Or Less"),
           age4 = fct_relevel(as_factor(age4), "18-29"),
           income3 = fct_relevel(as_factor(income3), "Less than 50k"),
           internet_skills = fct_relevel(as_factor(internet_skills), "Low Internet Skills"))
  
  return(df)
}

## prep data 
survey_full <- prep_data(survey_full)
survey_oversample <- prep_data(survey_oversample)

```

## Nondelivery + Banking

```{r}
## Set Colors for all models 

values = ggsci::pal_lancet()(6)

categories <- fullsample_results %>% filter(term != "(Intercept)") %>% 
  pull(category)

consistent_colors <- setNames(values, levels(as.factor(categories)) )


## pooled model
nondelivery_scam_model <- glm(payment_victim ~ racethnicity + gender + age4 + educ + income3 + internet_skills, family = "binomial", data = survey_full, weight = weight)

## pooled model
nondelivery_scam_model_results <-tidy(nondelivery_scam_model) %>%  
  mutate(odds_ratio = exp(estimate),
         p.value = round(p.value, 3)) %>% 
  mutate(category = case_when(
    str_detect(term, "racethnicity") ~ "Race/Ethnicity",
    str_detect(term, "income3") ~ "Income",
    str_detect(term, "educ") ~ "Education",
    str_detect(term, "age4") ~ "Age",
    str_detect(term, "gender") ~ "Gender",
    TRUE ~ "Internet Skills"
  )) %>% 
  mutate(term = prefix_strip(term, "racethnicity"),
         term = prefix_strip(term, "Income3"),
         term = prefix_strip(term, "educ"),
         term = prefix_strip(term, "Age4"),
         term = prefix_strip(term, "gender"),
         term = prefix_strip(term, "internet_skills"))



common_incidence_model_plot <- nondelivery_scam_model_results %>% 
  filter(term != "(Intercept)") %>% 
  mutate(lower = exp(estimate-1.96*std.error),
         upper = exp(estimate + 1.96*std.error)) %>% 
  ggplot(aes(x = odds_ratio,
             y = reorder(term, odds_ratio),
             xmin = lower,
             xmax = upper,
             color = category)) + 
  geom_pointrange() + 
  cowplot::theme_cowplot() + 
  geom_vline(xintercept = 1, linetype = "dashed")+ 
  scale_x_log10() + 
  labs(x = "Odds Ratio",
       y = "",
       title = "Banking + Non-Delivery") + 
  scale_color_manual(values = consistent_colors) + 
  theme(legend.position = "none")

common_incidence_model_plot
```

## Overpayment + Non-Payment

```{r}
## pooled model
payment_scam_model <- glm(seller_victim ~ racethnicity + gender  + age4 + income3 + educ , family = "binomial", data = survey_oversample, weight = weight2)


## pooled model
payment_scam_model_results <- tidy(payment_scam_model) %>%  
  mutate(odds_ratio = exp(estimate),
         p.value = round(p.value, 3)) %>% 
  mutate(category = case_when(
    str_detect(term, "racethnicity") ~ "Race/Ethnicity",
    str_detect(term, "income3") ~ "Income",
    str_detect(term, "educ") ~ "Education",
    str_detect(term, "age4") ~ "Age",
    str_detect(term, "gender") ~ "Gender",
    TRUE ~ "Internet Skills"
  )) %>% 
  mutate(term = prefix_strip(term, "racethnicity"),
         term = prefix_strip(term, "Income3"),
         term = prefix_strip(term, "educ"),
         term = prefix_strip(term, "Age4"),
         term = prefix_strip(term, "gender"))

rare_incidence_model_plot_sell <- payment_scam_model_results %>% 
  filter(term != "(Intercept)") %>% 
  mutate(lower = exp(estimate-1.96*std.error),
         upper = exp(estimate + 1.96*std.error)) %>% 
  ggplot(aes(x = odds_ratio,
             y = reorder(term, odds_ratio),
             xmin = lower,
             xmax = upper,
             color = category)) + 
  geom_pointrange() + 
  cowplot::theme_cowplot() + 
  geom_vline(xintercept = 1, linetype = "dashed")+ 
  scale_x_log10() + 
  labs(x = "Odds Ratio",
       y = "",
       title = "Nonpayment + Overpayment") + 
  scale_color_manual(values = consistent_colors) + 
  theme(legend.position = "null")

rare_incidence_model_plot_sell
```


```{r}
## pooled model
payment_extortion_model <- glm(scam_victim ~ racethnicity + gender + age4 + income3 + educ, family = "binomial", data = survey_oversample, weight = weight2)

## pooled model
payment_extortion_model_results <- tidy(payment_extortion_model) %>%  
  mutate(odds_ratio = exp(estimate),
         p.value = round(p.value, 3)) %>% 
  mutate(category = case_when(
    str_detect(term, "racethnicity") ~ "Race/Ethnicity",
    str_detect(term, "income3") ~ "Income",
    str_detect(term, "educ") ~ "Education",
    str_detect(term, "age4") ~ "Age",
    str_detect(term, "gender") ~ "Gender",
    TRUE ~ "Internet Skills"
  )) %>% 
  mutate(term = prefix_strip(term, "racethnicity"),
         term = prefix_strip(term, "Income3"),
         term = prefix_strip(term, "educ"),
         term = prefix_strip(term, "Age4"),
         term = prefix_strip(term, "gender"))

rare_incidence_model_extortion <- payment_extortion_model_results %>% 
  filter(term != "(Intercept)") %>% 
  mutate(lower = exp(estimate-1.96*std.error),
         upper = exp(estimate + 1.96*std.error)) %>% 
  ggplot(aes(x = odds_ratio,
             y = reorder(term, odds_ratio),
             xmin = lower,
             xmax = upper,
             color = category)) + 
  geom_pointrange() + 
  cowplot::theme_cowplot() + 
  geom_vline(xintercept = 1, linetype = "dashed")+ 
  scale_x_log10() + 
  labs(x = "Odds Ratio",
       y = "",
       title = "Advanced Fee + Extortion") + 
  scale_color_manual(values = consistent_colors) + 
  theme(legend.position = "bottom", legend.title = element_blank())

rare_incidence_model_extortion
```

```{r}
legend <- cowplot::get_legend(
  # create some space to the left of the legend
  rare_incidence_model_plot)

pgrid <- cowplot::plot_grid(common_incidence_model_plot, rare_incidence_model_plot_sell, rare_incidence_model_extortion +
  theme(legend.position = "none"), ncol = 1, labels = "auto")

p <- cowplot::plot_grid(pgrid, legend, nrow = 2, rel_heights = c(1, .1))

ggsave(plot = p, filename = "../figures/fig-demographic-models.pdf", height = 14, width = 8)
```



